### 2018-08-07 paper/sphinxes.tex
more edits, packet to message, sphinxes

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security.
Sphinx only provides one node per onion layer; in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
% AL: Bounded random-walk....
As such, Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/OR-POR.png}
  \caption{\label{fig:OR-POR}%
    Illustration of the conceptual difference between traditional onion routing 
    and mixing (top) and \ac{POR} (bottom).
    %\commentDaniel{This figure should be fixed, issue \#42.}
  }
\end{figure}

@@

We will now extend Sphinx to do \ac{POR}: instead of providing only \(d_{i+1}\) 
in \(\beta_i\), we will have a set \(\{d_{i+1}^{(1)}, \dotsc, d_{i+1}^{(m)}\}\) 
of \(m\) alternative next nodes.
This means that all \(m\) nodes must be able to compute the same shared secret 
\(s_{i+1}\).
We do this by adding one layer of indirection.

@@

\subsubsection{Sphinxes algorithms and \acf*{POR}}

@@

  \item \(\N\subset \bin^\kappa\) is a set of node identifiers.
    Each node \(n\in \N\) has a private key \(\sk_n\in \ZZ_q^*\) and a public 
    key \(\pk_n = g^{\sk_n}\in \G^*\).
    We assume that the identifier--public-key pairs, \((n, \pk_n)\), are 
    distributed.
    (Sphinx made a difference between nodes and destinations, \ie the set 
    \(\D\) such that \(\D\cap \N = \emptyset\) and \(\D\cup \N\) is prefix 
    free, see~\cite{Sphinx} for details.
    We could do the same adoption, but we do not need that for the purposes of 
    this paper.)
    We have two special node identifiers:
    \(\nullnode\in \N\) is the null-node identifier, indicating an empty 
    address.
    \(\rdvnode\in \N\) is the rendezvous-node identifier, indicating that the 
    current node is a rendezvous node and that the payload is \iac{POR} route 
    to forward.

@@

@@

This algorithm creates a header for \iac{POR}.
It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
set of addresses and keys for each layer instead of only one address and key.
Also, we do not distinguish between addresses of destinations and routers.

The algorithm takes as input a unique identifier \(I\in \bin^\kappa\) and a set 
of layers \(L = \{L_0, \dotsc, L_\nu\}\) such that \(\nu+1\leq r\).
The last layer, \(L_\nu\), should be either \(\{\nullnode\}\) or 
\(\{\rdvnode\}\) to terminate the routing.

@@

Next we need to compute the padding \(\phi_i\) for each layer \(i\).
We must do this to predict the padding introduced at each layer so that we 
can compute the correct \acp{MAC} (\(\gamma_i\)).
The padding for the outmost layer (layer 0) is the empty string, thus \(\phi_0 
  \gets \epsilon\).
Then, for layers \(1\leq i\leq \nu\), we get
\begin{multline*}
  \phi_i\gets \left\{\phi_{i-1}\concat 0_{w_H\kappa}\right\}\oplus \\
  \left\{\prg\left(\hash_\prg\left(s_{i-1}\right)\right)_{[(w_H(r-i)+3)\kappa..(2r+3)\kappa-1]}\right\}.
\end{multline*}

Next we will use the above computations to compute the mix headers \(M_i = 
  (\alpha_i, \beta_i, \gamma_i)\).
\(\alpha_i\) was computed above, so we will compute \(\beta_i\) and 
\(\gamma_i\).
We must compute \(\beta_i\) in reverse order.
We let \(\beta_{\nu} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu < i\leq 
  0\), we let
\begin{align*}
  \beta_i &\gets \left\{L_{i+1}\concat C_{i+1}\concat \gamma_{i+1}\concat 
    (\beta_{i+1})_{[0..(w_H r-1)\kappa-1]}\right\}, \\
  \gamma_i &\gets \mac\left( \hash_\mac\left(s_i\right), \beta_i \right).
\end{align*}

@@

If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
If \(t\) is already in the table of seen packets, drop the packet.
Otherwise, add \(t\) to the table and decrypt \(\beta\):
\begin{equation*}
  L'\concat C'\concat \gamma'\concat \beta'\gets \{\beta\concat 0_{w_H 
    \kappa}\}
  \oplus \prg(\hash_\prg(s_i))
\end{equation*}

>>>>

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security. \sonja{what about the CL properties?}
Sphinx only provides one node per onion layer; in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
% AL: Bounded random-walk....
As such, Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/OR-POR.png}
  \caption{\label{fig:OR-POR}%
    Illustration of the conceptual difference between traditional onion routing 
    and mixing (top) and \ac{SPOR} (bottom).
    %\commentDaniel{This figure should be fixed, issue \#42.}
  }
\end{figure}

@@

We will now extend Sphinx to do \ac{SPOR}: instead of providing only \(d_{i+1}\) 
in \(\beta_i\), we will have a set \(\{d_{i+1}^{(1)}, \dotsc, d_{i+1}^{(m)}\}\) 
of \(m\) alternative next nodes.
This means that all \(m\) nodes must be able to compute the same shared secret 
\(s_{i+1}\).
We do this by adding one layer of indirection.

@@

\subsubsection{Sphinxes algorithms and \acf*{SPOR}}

@@

  \item \(\N\subset \bin^\kappa\) is a set of node identifiers.
    Each node \(n\in \N\) has a private key \(\sk_n\in \ZZ_q^*\) and a public 
    key \(\pk_n = g^{\sk_n}\in \G^*\).
    We assume that the identifier--public-key pairs, \((n, \pk_n)\), are 
    distributed.
    (Sphinx made a difference between nodes and destinations, \ie the set 
    \(\D\) such that \(\D\cap \N = \emptyset\) and \(\D\cup \N\) is prefix 
    free, see~\cite{Sphinx} for details.
    We could do the same adoption, but we do not need that for the purposes of 
    this paper.)
    We have two special node identifiers:
    \(\nullnode\in \N\) is the null-node identifier, indicating an empty 
    address.
    \(\rdvnode\in \N\) is the crossover-node identifier, indicating that the 
    current node is the node at the end of one leg of a route that needs to cross
   over to another, and that the payload is \iac{SPOR} route 
    for forwarding.

@@

We keep the nomenclature of mix headers and messages from Sphinx for
clarity but later apply them to onions and file chunks, repectively.

@@

This algorithm creates a header for \iac{SPOR}.
It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
set of addresses and keys for each layer instead of only one address and key.
Also, we do not distinguish between addresses of destinations and routers.

The algorithm takes as input a unique identifier \(I\in \bin^\kappa\) and a set 
of layers \(L = \{L_0, \dotsc, L_\nu\}\) such that \(\nu+1\leq r\).
The last layer, \(L_\nu\), should be either \(\{\nullnode\}\) or 
\(\{\rdvnode\}\) to terminate the routing. \sonja{define v(nu)}

@@

Next we need to compute the padding \(\phi_i\) for each layer \(i\).
We must do this to predict the padding introduced at each layer so that we 
can compute the correct \acp{MAC} (\(\gamma_i\)).
The padding for the outermost layer (layer 0) is the empty string, thus \(\phi_0 
  \gets \epsilon\).
Then, for layers \(1\leq i\leq \nu\), we get
\begin{multline*}
  \phi_i\gets \left\{\phi_{i-1}\concat 0_{w_H\kappa}\right\}\oplus \\
  \left\{\prg\left(\hash_\prg\left(s_{i-1}\right)\right)_{[(w_H(r-i)+3)\kappa..(2r+3)\kappa-1]}\right\}.
\end{multline*}

Next we will use the above computations to arrive at the mix headers \(M_i = 
  (\alpha_i, \beta_i, \gamma_i)\).
\(\alpha_i\) was computed above, so we will compute \(\beta_i\) and 
\(\gamma_i\).
We must compute \(\beta_i\) in reverse order. \sonja{why? layering?}
We let \(\beta_{\nu} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu < i\leq 
  0\), we let
\begin{align*}
  \beta_i &\gets \left\{L_{i+1}\concat C_{i+1}\concat \gamma_{i+1}\concat 
    (\beta_{i+1})_{[0..(w_H r-1)\kappa-1]}\right\}, \\
  \gamma_i &\gets \mac\left( \hash_\mac\left(s_i\right), \beta_i \right).
\end{align*}

@@

If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
If \(t\) is already in the table of seen messages, drop the message.
Otherwise, add \(t\) to the table and decrypt \(\beta\):
\begin{equation*}
  L'\concat C'\concat \gamma'\concat \beta'\gets \{\beta\concat 0_{w_H 
    \kappa}\}
  \oplus \prg(\hash_\prg(s_i))
\end{equation*}
